MSDS 7333 Case Study 06

### 2017-06-18 MSDS7333_CaseStudy06_MBaldree_BBrock_TElkins_AKelly.Rmd
Created and filled out the intro. Needs revision

2. Implement alternative k-nearest precition method using weights on received signal strength.
* *For what range of values of weights are you able to obtain better prediction values than for the unweighted approach?*
* *Use calcError() to compare approaches*

## Introduction
(insert text here)

>>>>

2. Implement alternative k-nearest precition method using weights on received signal strength.
* *For what range of values of weights are you able to obtain better prediction values than for the unweighted approach?*
* *Use calcError() to compare approaches*
<font color = "green">

## Introduction
#### *Explain the case study*
- Discuss the goal of the case study

For this case study, the overall goal is to use K-Nearest Neighbors (kNN) and an alternative weighted method to be able to determine how different handheld devices moved through a building <font color = "red">(at Dartmouth. Let's confirm this and add some more detail)</font>. This can be achieved with an analysis of how the different Media Access Control (MAC) addresses for each of the devices interacted with the Access Points (APs) of the building. In this case, the APs are routers with known locations throughout the building.

- Discuss the different Access points and MAC Addresses

The access points as stated above allow for the tracking of the devices, thanks to the history of times, signal strengths and angles recorded for each MAC address with respect to each access point.<font color = "red">&larr;(consider fragmenting this sentence)</font> From the information that has been given, there are known to be six APs on the building floor in question. However, this is a problem since there are seven APs recorded. To determine which AP to exclude from the analysis, we will need to compare these two addresses:

    chosenAP   = "00:0f:a3:39:e1:c0"
    rejectedAP = "00:0f:a3:39:dd:cd"

and decide which to exclude and why.

  - Discuss why we're trying to remove one

Removing one of these APs will allow us to remove noise from the resulting model. Since only six APs are recorded as existing on the floor, the presence of a seventh points to external interference. Once the superfluous address has been identified, we will execute testing to determine whether there will be any benefit added to the model by keeping or excluding said data. This decision will ultimately lead to a better prediction of location of each device within this floorplan.

- BRIEF overview of K-Nearest Neighbors

K-Nearest Neighbors (kNN) is an ideal method to use in this case as the goal is to be able to predict the path of each device on their journey through the building. To utilize this method, we use separate testing and training data. The training data are known observations from well documented locations of both the handheld devices and APs. These locations are represented by the angle at which the AP received the signal from the device as well as the overall signal strength received.

With this training data, each observation is evaluated along with the observations which occur in the general vicinity in the training data. These occurrences allow for the different probabilities of occurrence to be proposed through the model. Once this model has been generated for k neighbors, it is then tested against the unobserved test data and adapted to suit what actually occurs. This allows for an accurate gauge of accuracy of the model and is recreated for a span of possible k neighbors to exhaust the total possible number of observations.

- Discuss the alternative weighted method.

In contrast to the kNN method, another option to explore is a weighted method based on the signal strength received at the access point. This method involves defining a new metric where the weight of each observation is inversely proportional to the distance from the test observation. From a topographical standpoint, the observations which are closest to the observation will have a much higher influence than those which exist further away.

- Discuss potential for prediction and what we expect to come of this.

The evaluation of this data will allow us to determine which data will be critical to the creation of an accurate model and which will not. Since we have six access points and seven addresses, this thorough investigation will help us decide which address is simply an external interference and if it is beneficial to keep involving said data. As a result, we expect to have a more thorough understanding of the difference between k-Nearest Neighbors and the weighted alternative.

</font>
***
